Supporting Information for "Ship-based lidar evaluation of Southern Ocean low clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses"

### 2025-07-21 si_rev1.tex
Small fixes
Various submission-related changes

\usepackage{xr}
\externaldocument{manuscript_agu_rev1}

@@

\title{Supporting Information for "Ship-based lidar evaluation of Southern Ocean low clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses"}

@@

\begin{figure}[t]
\centerline{
\includegraphics[width=1.2\textwidth]{img/rs_thetav_hur_cloud.pdf}
}
\caption{
The same as Fig.~\ref{fig:potential-temperature}, but only for profiles that contain \textbf{(a)} fog, \textbf{(b)} cloud at 500~m, and \textbf{(c)} cloud at 1.5~km.
}
\label{fig:rs-thetav-hur-cloud}
\end{figure}

\begin{figure}[t]
\centerline{
\includegraphics[width=1.2\textwidth]{img/rs_thetav_hist.png}
}
\caption{
The same as Fig.~\ref{fig:rs-hur-hist}, but for virtual potential temperature.
}
\label{fig:rs-thetav-hist}
\end{figure}

>>>>

@@

\title{Supporting Information for "Ship-based lidar evaluation of Southern Ocean low clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses"}

@@

\begin{figure}[t]
\centerline{
\includegraphics[width=1.2\textwidth]{img/rs_thetav_hur_cloud.pdf}
}
\caption{
The same as Fig.~9, but only for profiles that contain \textbf{(a)} fog, \textbf{(b)} cloud at 500~m, and \textbf{(c)} cloud at 1.5~km.
}
\label{fig:rs-thetav-hur-cloud}
\end{figure}

\begin{figure}[t]
\centerline{
\includegraphics[width=1.2\textwidth]{img/rs_thetav_hist.png}
}
\caption{
The same as Fig.~11, but for virtual potential temperature.
}
\label{fig:rs-thetav-hist}
\end{figure}
